ML Estimation of Matrix t Distributions with Expectation Maximization

### 2016-12-11 paper.tex
Improve introduction

\paragraph{Introduction}
Matrix--$t$ distributions have been applied to several predictive
problems, such as spatial interpolation applied to the prediction of
pollution concentration \citep{KIBRIA2006785}, recommendation systems
\citep{NIPS2007_3203}, and ...

@@

The derivation of EM formulae for matrix--$t$ distributions is mainly based on the following integral identity:

>>>>

\paragraph{Introduction}
Matrix--$t$ distributions have been applied to several predictive
problems, such as spatial interpolation applied to the prediction of
pollution concentration \citep{KIBRIA2006785}, recommendation systems
\citep{NIPS2007_3203}. In these situations it is necessary to obtain
the parameters of the metrix--$t$ distribution (consisting of the
number of degrees of freedom, a location matrix and two scale
matrices) that describe a set of given matrix valued observations.
While the exact formulae for Maximum Likelihood Estimation (MLE) are
unwieldy and slow to compute, the problem can be simplified if instead
we obtain the distribution parameters using Expectation-Maximization
(EM). We obtain can obtain the EM expressions by viewing the
matrix--$t$  distribution as a matrix-normal distribution where one of
the scale matrices is sampled from a Wishart distribution.

@@

The derivation of the EM formulae is mainly based on the following integral identity:
